GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2025-07-04 writeUps/paper.tex
Updates from Overleaf

\begin{figure}[!ht]
  \centering
  \includegraphics[width=4.5in]{../simFigs/biasSEbyB1N.jpg}
  \caption{Empirical bias and standard error of \textsc{geepers} and Mixture estimates of $\eff1$ as sample size per treatment group $n$ or $\alpha$ varied. There were 500 replications for each $n$ or $\alpha$. Other factors were held fixed at the noted values.}
  \label{fig:alphan}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{../simFigs/biasSEbyB1.jpg}
  \caption{Empirical bias and standard error of M- and Mixture estimates of $\muc1$ as $\alpha$ varies from 0.1 to 1. There were 500 replications for each $n$. Other factors were held fixed at the noted values.}
  \label{fig:alpha}
\end{figure}

@@

\section*{Replication Materials}
Replication materials can be found at
\url{https://osf.io/fu2sv/?view_only=b2baebc2f3054ef796717863e4a9662f}.

>>>>

% \begin{figure}[!ht]
%   \centering
%   \includegraphics[width=4.5in]{../simFigs/biasSEbyB1N.jpg}
%   \caption{Empirical bias and standard error of \textsc{geepers} and Mixture estimates of $\eff1$ as sample size per treatment group $n$ or $\alpha$ varied. There were 500 replications for each $n$ or $\alpha$. Other factors were held fixed at the noted values.}
%   \label{fig:alphan}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics{../simFigs/biasSEbyB1.jpg}
%   \caption{Empirical bias and standard error of M- and Mixture estimates of $\muc1$ as $\alpha$ varies from 0.1 to 1. There were 500 replications for each $n$. Other factors were held fixed at the noted values.}
%   \label{fig:alpha}
% \end{figure}

@@

\section*{Replication Materials}
\sloppy
Replication materials can be found at
\url{https://osf.io/fu2sv/?view_only=b2baebc2f3054ef796717863e4a9662f}.
